Centralizers of higher enveloping algebras and their large $N$ limits

### 2019-05-17 frame.tex
my changs

\begin{cor}
\label{thm: center}
The center of the enveloping $E_n$ algebra $\UU_n\fg$ is the $E_n$ algebra $\clies(\fg, \UU_n\fg)$. 
When $k$ is $\RR$ or $\CC$, the 
center is modeled by the locally constant factorization algebra that assigns
\[
\clies(\fg \otimes \Omega^*(U), \cliels( \fg \otimes \Omega^*_c(U)))
\]
to each open set $U \subset \RR^n$.
\end{cor}

\owen{Add remark for ", which by Dunn's additivity theorem has in fact a natural $E_{n+1}$ algebra structure."}

@@

@@

\begin{thm}
There is a commuting square of adjunctions
\[
\begin{tikzcd}
\Alg_\Lie(\Mod_k) \arrow[r, bend left=20, shift left=.5ex,"\UU_n"] \arrow[dd] & \Alg_{E_n}(\Mod_k) \arrow[l, shift left=.5ex, "\oblv"] \arrow[dd]\\
&\\
\Mod_k \arrow[r, bend left=20, shift left=.5ex, "\Sigma^{1-n}"] \arrow[uu, bend left=20, shift left=.5ex, "\Free_\Lie"] & \Mod_k \arrow[l, shift left=.5ex,"\Sigma^{n-1}"] \arrow[uu, bend right=20, shift right=.5ex, "\Free_{E_n}"']
\end{tikzcd}
\]

\mahmoud{explain what oblv stands for}
where $\Sigma$ denotes suspension \owen{because tikzcd does weird things with ``[1-n]'' instead}, \mahmoud{earlier we denoted the shift by [n]. should we use $\Sigma^n$ everywhere?}.
(Curving arrows denote left adjoints.)

@@

\begin{dfn}
For a map $f: A \to B$ of $E_n$ algebras in $\cC$, 
the {\em centralizer} ${\frak Z}_{E_n}(f)$ is the $E_n$ algebra in $\cC$ that is universal among those that fit in a commuting diagram
\[
\begin{tikzcd}
& {\frak Z}_{E_n}(f) \otimes A \arrow[dr] & \\
A \arrow[ur, "u"] \arrow[rr, "f"] && B
\end{tikzcd}
\]
where $u$ is induced by the identity map $1_\cC \to {\frak Z}_{E_n}(f)$. The {\em center} of an $E_n$ algebra $A$ is the centralizer of its identity morphism $\id_A: A \to A$.
\end{dfn}
When $n=1$ and $\cC$ is the category of vector spaces, the centralizer of $f: A \to B$ consists of the subspace of elements of $B$ that commute with the image $f(A)$ inside~$B$. Thus, the center of $A$ agrees with the traditional notion. See Theorem 5.3.1.30 of~\cite{LurieHA}, or Proposition 6.22 in~\cite{GTZ3}, for an alternative characterization.

\begin{prp}
The centralizer ${\frak Z}_{E_n}(f)$ can be identified with the classifying object for maps from $A$ to $B$ in the $\infty$-category $\Mod^{E_n}_A(\cC)$. \mahmoud{we should probably spell out the meaning of the classifying object in this case to make it obvious that the centralizer is the classifying object}
\end{prp}

>>>>

\begin{cor}
\label{thm: center}
The center ${\frak Z}_{E_n}(\UU_n\fg)$ of the enveloping $E_n$ algebra $\UU_n\fg$ is the $E_n$ algebra $\clies(\fg, \UU_n\fg)$. 
When $k$ is $\RR$ or $\CC$, the 
center is modeled by the locally constant factorization algebra that assigns
\[
\clies(\fg \otimes \Omega^*(U), \cliels( \fg \otimes \Omega^*_c(U)))
\]
to each open set $U \subset \RR^n$.
\end{cor}

In fact, ${\frak Z}_{E_n}(\UU_n\fg)$ has a natural $E_{n+1}$ algebra structure, 
as shown in \cite{LurieHA, GTZ}, 
but we will not examine it here.

@@

As another consequence of the theorem, we note that we recover an explicit model for the Koszul dual to the enveloping algebra. 
Namely, take $B$ to be the unit $E_n$ algebra $k$ (alternatively, take the enveloping $E_n$ algebra of the trivial Lie algebra $\fh = 0$).

\begin{cor}
\label{thm: koszul}
The $E_n$ Koszul dual of the enveloping $E_n$ algebra $\UU_n\fg$ is the underlying $E_n$ algebra of the $\clies(\fg)$. 
When $k$ is $\RR$ or $\CC$, the 
center is modeled by the locally constant factorization algebra that assigns
\[
\clies(\fg \otimes \Omega^*(U)))
\]
to each open set $U \subset \RR^n$.
\end{cor}

@@

\begin{thm}
There is a commuting square of adjunctions
\[
\begin{tikzcd}
\Alg_\Lie(\Mod_k) \arrow[r, bend left=20, shift left=.5ex,"\UU_n"] \arrow[dd, "\oblv"] & \Alg_{E_n}(\Mod_k) \arrow[l, shift left=.5ex, "\oblv"] \arrow[dd, swap, "\oblv"]\\
&\\
\Mod_k \arrow[r, bend left=20, shift left=.5ex, "\text{$[1-n]$}"] \arrow[uu, bend left=20, shift left=.5ex, "\Free_\Lie"] & \Mod_k \arrow[l, shift left=.5ex, "\text{$[n-1]$}"] \arrow[uu, bend right=20, shift right=.5ex, "\Free_{E_n}"']
\end{tikzcd}
\]
where $\oblv$ denotes a forgetful functor.
(Curving arrows denote left adjoints.)

@@

\begin{dfn}
For a map $f: A \to B$ of $E_n$ algebras in $\cC$, 
the {\em centralizer} ${\frak Z}_{E_n}(f)$ is the $E_n$ algebra in $\cC$ that is universal among those that fit in a commuting diagram
\[
\begin{tikzcd}
& {\frak Z}_{E_n}(f) \otimes A \arrow[dr] & \\
A \arrow[ur, "u"] \arrow[rr, "f"] && B
\end{tikzcd}
\]
where $u$ is induced by the identity map $1_\cC \to {\frak Z}_{E_n}(f)$. The {\em center} of an $E_n$ algebra $A$ is the centralizer of its identity morphism $\id_A: A \to A$.
\end{dfn}
When $n=1$ and $\cC$ is the category of vector spaces, the centralizer of $f: A \to B$ consists of the subspace of elements of $B$ that commute with the image $f(A)$ inside~$B$. Thus, the center of $A$ agrees with the traditional notion. See Theorem 5.3.1.30 of~\cite{LurieHA}, or Proposition 6.22 in~\cite{GTZ3}, for an alternative characterization,
as follows.

\begin{prp}
The centralizer ${\frak Z}_{E_n}(f)$ can be identified with the classifying object for maps from $A$ to $B$ in the $\infty$-category~$\Mod^{E_n}_A(\cC)$.
\end{prp}

Here ``classifying object'' means an internal hom object, so that a map from $M$ to ${\frak Z}_{E_n}(f)$ in $\Mod^{E_n}_A(\cC)$ corresponds to a map from $M \otimes A$ to $B$ in $\Mod^{E_n}_A(\cC)$. 
(More carefully, there is an equivalence of the appropriate mapping spaces in that category.)
\owen{We should double check this.}
